
set.seed(13)
suppressPackageStartupMessages(library("knitr"))
suppressPackageStartupMessages(library("kableExtra"))
suppressPackageStartupMessages(library("plotrix"))
suppressPackageStartupMessages(library("latex2exp"))

# source functions
source("scores_loadings_functions.R")

# colors and color names
axis2_col = "#3db7ed"
axis2_colname = "light blue"
axis1_col = "#f748a5"
axis1_colname = "pink"
loadings_col = "#359b73"
loadings_colname = "green"
origdata_col = "#000000"
origdata_colname = "black"

data_set_1 = generate_data(size = 10)
rotate0 = rot_axes(angle = 0, file = data_set_1)
rotate15 = rot_axes(angle = 15, file = data_set_1)
rotate20 = rot_axes(angle = 20, file = data_set_1)
rotate30 = rot_axes(angle = 30, file = data_set_1)
rotate40 = rot_axes(angle = 40, file = data_set_1)
rotate45 = rot_axes(angle = 45, file = data_set_1)
rotate60 = rot_axes(angle = 60, file = data_set_1)
rotate75 = rot_axes(angle = 75, file = data_set_1)
rotate80 = rot_axes(angle = 80, file = data_set_1)

```{r fig-origData, fig.align="center", fig.cap="Scatterplot of variable 1 and variable 2 for our eight samples. The dashed lines are the original axes with variable 1 shown in pink and variable 2 shown in blue."}

plot_rot_axes(rotate0, show_rotated = FALSE, show_full_legend = FALSE,
              show_scores = FALSE, show_simple_legend = FALSE,
              show_loadings = FALSE, show_title = FALSE, show_projections = FALSE)
legend(x = "topleft", legend = c("variable 1", "variable 2"),
       lty = 2, lwd = 1, col = c(axis1_col,axis2_col), bty = "n")

```{r rotate20, fig.align="center", fig.cap="Rotating the original axes by 20$^\\circ$ gives the axes shown as solid lines. The small points in pink and in blue are the projections of the original data onto the rotated axes. The gray lines serve as a guide to illustrate the projections for one data point."}
plot_rot_axes(rotate20, show_loadings = FALSE, show_simple_legend = FALSE,
              show_full_legend = FALSE, show_full_axes_legend = TRUE,
              show_scores = TRUE, show_projections = TRUE)

```{r rotate60, fig.align="center", fig.cap="Rotating the original axes by 60$^\\circ$ maximizes the variance along one of the two rotated axes; the line in pink is the first principal component axis and the line in blue is the second principal component axis.  The gray lines serve as a guide to illustrate the projections for one data point."}
plot_rot_axes(rotate60, show_loadings = FALSE, show_simple_legend = FALSE,
              show_full_legend = TRUE, show_full_axes_legend = FALSE,
              show_scores = TRUE, show_projections = TRUE)
```

```{r rotate60-loadings, fig.align="center", fig.cap="Illustration showing the loadings for the first principal component axis."}
plot_rot_axes(rotate60, show_loadings = TRUE, show_simple_legend = FALSE,
              show_full_legend = TRUE, show_full_axes_legend = FALSE,
              show_scores = TRUE, show_projections = TRUE)
